Effect of character correlation

### 2017-09-18 Analysis/EffectCorrelationStats.Rmd
stats pooled draft

>>>>

Effect of character correlation per scenario
-----------------

```{r}
## Pulling the data per scenario
max_RF_norm <- pool.distribution(whole_data, param = "maxi", metric = "RF", best = "norm")
min_RF_norm <- pool.distribution(whole_data, param = "mini", metric = "RF", best = "norm")
rand_RF_norm <- pool.distribution(whole_data, param = "rand", metric = "RF", best = "norm")
scenario_RF_norm <- matrix(data = c(max_RF_norm, min_RF_norm, rand_RF_norm),
                           ncol = 3, dimnames = list(c(), c("max", "min", "rand")))

max_RF_null <- pool.distribution(whole_data, param = "maxi", metric = "RF", best = "rand")
min_RF_null <- pool.distribution(whole_data, param = "mini", metric = "RF", best = "rand")
rand_RF_null <- pool.distribution(whole_data, param = "norm", metric = "RF", best = "rand")
scenario_RF_null <- matrix(data = c(max_RF_null, min_RF_null, rand_RF_null),
                           ncol = 3, dimnames = list(c(), c("max", "min", "norm")))

max_Tr_norm <- pool.distribution(whole_data, param = "maxi", metric = "Tr", best = "norm")
min_Tr_norm <- pool.distribution(whole_data, param = "mini", metric = "Tr", best = "norm")
rand_Tr_norm <- pool.distribution(whole_data, param = "rand", metric = "Tr", best = "norm")
scenario_Tr_norm <- matrix(data = c(max_Tr_norm, min_Tr_norm, rand_Tr_norm),
                           ncol = 3, dimnames = list(c(), c("max", "min", "rand")))

max_Tr_null <- pool.distribution(whole_data, param = "maxi", metric = "Tr", best = "rand")
min_Tr_null <- pool.distribution(whole_data, param = "mini", metric = "Tr", best = "rand")
rand_Tr_null <- pool.distribution(whole_data, param = "norm", metric = "Tr", best = "rand")
scenario_Tr_null <- matrix(data = c(max_Tr_null, min_Tr_null, rand_Tr_null),
                           ncol = 3, dimnames = list(c(), c("max", "min", "norm")))

op <- par(mfrow = c(2,2))#, mar = c(2, 4, 1, 2))
cols <- c("red", "orange", "green3", "lightgreen", "blue", "lightblue")

boxplot(scenario_RF_norm, las = 1, horizontal = TRUE, xlab = "")

plot.results.single(t25_list, metric = 2, what = "best",
    legend = TRUE, NTS = TRUE, xlab = "", ylab = "RF for 25 taxa",
    axislab = FALSE)
plot.results.single(t75_list, metric = 2, what = "best", ylab = "RF for 75 taxa",
    xlab = "", axislab = FALSE, NTS = TRUE)
plot.results.single(t150_list, metric = 2, what = "best",
    ylab = "RF for 150 taxa", NTS = TRUE)
par(op)

boxplot(scenario_RF_norm, col = )
```

Effect of character correlation per number of character
-----------------

Effect of character correlation per number of taxa
-----------------

Effect of character correlation per methods
-----------------
